Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-22 main_paper.tex
Table redesign
This commit tweaks the table layout to make the different statistics
more directly comparable to each other. It also makes a few cosmetic
changes.

\begin{table}[ht] \label{Tb1}
	\caption{Summary of estimates ($p = 1, q = 2$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
		\hline
	\end{tabular}
\end{table}

\begin{table}[ht]\label{Tb2}
	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
	\centering
	\begin{tabular}{ccccccc}
		\hline
		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
		\hline
		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
		&&&&&& \\
		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
		\hline
	\end{tabular}
\end{table}
As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

>>>>

\begin{table}[t] \label{Tb1}
\centering
\begin{tabular}{rrrrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
  \bottomrule
\end{tabular}
\caption{Summary of estimates ($p = 1, q = 2$)}
\end{table}

As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

\begin{table}[t]\label{Tb2}
\centering
\begin{tabular}{rrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
  \bottomrule
\end{tabular}
\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
\end{table}
